Finding Sigma and Mu

### 2021-08-03 graphs_newt_snakes/find_params.Rmd
I added a legend to the find param r markdown (today I will be adding more explination). I am working ou the the population size problem in nospace slim. How many of the newts interact with the snakes?

@@

ggplot(my_grid, aes(x = Var1, y=Var2)) +
  geom_point(data=my_grid[my_grid$results <=5, ], aes(x = Var1, y=Var2), col="blue")+
  geom_point(data=my_grid[my_grid$results <=2, ], aes(x = Var1, y=Var2), col="green")+
  ggtitle("Value Combinations That Might Work") +
  xlab("Sigma") + ylab("Mu")+
  theme_bw()

@@

#2=sigma*sqrt(mu)*2*10^6
y_mu_2 = (2/(sigma*2*10^6))^2
y_mu_5 = (5/(sigma*2*10^6))^2
x_sigma_2 = 2/(sqrt(mu)*2*10^6)
x_sigma_5 = 5/(sqrt(mu)*2*10^6)
ggplot() +
  geom_line(aes(x = sigma, y=y_mu_5), col="blue")+
  geom_line(aes(x = sigma, y=y_mu_2), col="green")+
  geom_line(aes(x = x_sigma_5, y=mu), col="blue")+
  geom_line(aes(x = x_sigma_2, y=mu), col="green")+
  scale_y_log10()+
  #geom_point(data=my_grid[my_grid$results <=2, ], aes(x = Var1, y=Var2), col="green")+
  ggtitle("Value Combinations That Might Work") +
  xlab("Sigma") + ylab("Mu (log)")+ #xlim(0, 0.6)+
  theme_bw()

>>>>

# Different Combinations

Here I am using different values with the above formula to try to get the phenotypes of 5 and 2

@@

ggplot(my_grid, aes(x = Var1, y=Var2, colour = results)) +
  geom_point(data=my_grid[my_grid$results <=5, ], aes(x = Var1, y=Var2, colour="Less than 5"))+
  geom_point(data=my_grid[my_grid$results <=2, ], aes(x = Var1, y=Var2, colour="Less than 2"))+
  ggtitle("Value Combinations That Might Work") +
  xlab("Sigma") + ylab("Mu")+  
  theme_bw()+
  scale_color_manual(name = "Fake Phenotypes", values = c("Less than 5" = "blue", "Less than 2" = "green"))

@@

#2=sigma*sqrt(mu)*2*10^6
y_mu_2 = (2/(sigma*2*10^6))^2
y_mu_5 = (5/(sigma*2*10^6))^2
x_sigma_2 = 2/(sqrt(mu)*2*10^6)
x_sigma_5 = 5/(sqrt(mu)*2*10^6)
ggplot() +
  geom_line(aes(x = sigma, y=y_mu_5, colour="Less than 5"))+
  geom_line(aes(x = sigma, y=y_mu_2, colour="Less than 2"))+
  #lines are out of order, but the points line up. Looks Good!
  #geom_point(aes(x = x_sigma_5, y=mu), col="blue")+
  #geom_point(aes(x = x_sigma_2, y=mu), col="green")+
  scale_y_log10()+
  #geom_point(data=my_grid[my_grid$results <=2, ], aes(x = Var1, y=Var2), col="green")+
  ggtitle("Value Combinations That Might Work") +
  xlab("Sigma") + ylab("Mu (log)")+ #xlim(0, 0.6)+
  theme_bw()+
  scale_color_manual(name = "Fake Phenotypes", values = c("Less than 5" = "blue", "Less than 2" = "green"))
